TacticToe: Learning the Game of Tactics

### 2018-02-19 tactictoe_jv.tex
minor

\todoi{Rewrite the plan}
  To do this, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for a \emph{Monte Carlo tree search} that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a certified human-level proof composed of \holfour
  tactics.  The system is evaluated on a large set of theorems originating
  from \holfour (Section~\ref{s:experiments}).

@@

The application of tactic to a goal produces a list of goals. Each of the 
created goals can in turn be the input other tactics. Moreover, it is possible 
to try multiple tactics on the same goal. In order to keep track of the 
progress made so far from the initial goal we want to solve, we organize
goals and tactics into a graph with list of goals as nodes and tactics as edges
(See Definition~\ref{def:stree}).

In this section, we only give a description of the graph at a given 
moment of the search after a certain amount of tactic applications. 
The exploration of the tree is decided by MCTS algorithm in 
Section~\ref{sec:proofsearch}, which is guided by a tactic prediction algorithm 
presented in Section~\ref{sec:features}.

>>>>

\todoi{Rewrite the plan}
  To do this, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for a \emph{Monte Carlo tree search} that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics.  The system is evaluated on a large set of theorems originating
  from \holfour (Section~\ref{s:experiments}).

@@

The application of tactic to an initial conjecture produces a list of goals. 
Each of the created goals can in turn be the input other tactics. Moreover, it 
is possible to try multiple tactics on the same goal. In order to keep track of 
the progress made so far from the initial conjecture we want to solve, we 
organize goals and tactics into a graph with list of goals as nodes and tactics 
as edges (See Definition~\ref{def:stree}).

In this section, we only give a description of the graph at a given 
moment of the search after a certain amount of tactic applications. 
The exploration of the tree is decided by MCTS algorithm in 
Section~\ref{sec:proofsearch}, which is guided by a prediction algorithms 
presented in Section~\ref{sec:predictions}.
